Towards a miniKanren with fair search strategies

### 2019-05-22 Paper/paper.tex
NOTE swap back

Fair DFS (\DFSf) has fair \disj{} and unfair \conj{}. The 
implementation of \DFSf{} differs from \DFSi{}'s in 
\texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is changed to call a new and 
fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
immediately 
calls 
its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
\texttt{\#{}t}, which indicates that 
\texttt{s$^\infty$} and \texttt{t$^\infty$} haven't been swapped. The swapping 
happens at 
the third \texttt{cond} clause in the helper, where \texttt{s?} is updated 
accordingly. The first two \texttt{cond} clauses essentially copy the 
\texttt{car}s and stop recursion when one of the input spaces is obviously 
finite. The third clause, as we mentioned above, is just for swapping. When the 
fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
\texttt{t$^\infty$} are ended with a thunk and they have been swapped. In this 
case, a new thunk is constructed. Here changing the order of 
\texttt{t$^\infty$} and \texttt{s$^\infty$} won't hurt the fairness (though it 
changes the order of answers). We swap them back so that answers are 
produced in a more natural order.

\NOTE[DPF]{When or where do you swap them back?}

>>>>

Fair DFS (\DFSf) has fair \disj{} and unfair \conj{}. The 
implementation of \DFSf{} differs from \DFSi{}'s in 
\texttt{disj2} (Fig.~\ref{fDFS}). \texttt{disj2} is changed to call a new and 
fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
immediately 
calls 
its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
\texttt{\#{}t}, which indicates that 
\texttt{s$^\infty$} and \texttt{t$^\infty$} haven't been swapped. The swapping 
happens at 
the third \texttt{cond} clause in the helper, where \texttt{s?} is updated 
accordingly. The first two \texttt{cond} clauses essentially copy the 
\texttt{car}s and stop recursion when one of the input spaces is obviously 
finite. The third clause, as we mentioned above, is just for swapping. When the 
fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
\texttt{t$^\infty$} are ended with a thunk and they have been swapped. In this 
case, a new thunk is constructed. 
The new thunk swapped two search spaces back before recursion. This is 
unnecessary for fairness. We do it such that answers are produced in a more 
natural order.

% Here changing the order of 
% \texttt{t$^\infty$} and \texttt{s$^\infty$} won't hurt the fairness (though it 
% changes the order of answers). We swap them back so that answers are 
% produced in a more natural order.

\NOTE[DPF]{When or where do you swap them back?}
\NOTE[LKC]{fixed}
